---
title: "Individual project_ Harsha Kumar"
author: "hk425"
date: "2024-03-14"
output:
  html_document: default
  word_document: default
---

```{r message=FALSE, warning=FALSE}
#importing libraries
library(tidyverse)
library(seasonal)
library(fpp2)
library(ggplot2)

```

```{r message=FALSE, warning=FALSE}
#creating variables
USD_GBP <- read_csv('USD_GBP Historical Data monthly.CSV')
USD_AUD <- read_csv('USD_AUD Historical Data monthly.CSV')
USD_JPY <- read_csv('USD_JPY Historical Data monthly.CSV')
Dow_Jones<- read_csv('Dow Jones Industrial Average Historical Price Data monthly.CSV')
Nikkei_225 <-read_csv('Nikkei 225 Historical Price Data monthly.CSV')
FTSE_100 <- read_csv('FTSE 100 Historical Price Data monthly.CSV')
```



```{r}
#formating data
USD_GBP[['Date']]<- as.Date(USD_GBP[['Date']],format = "%d/%m/%Y")
USD_AUD[['Date']]<- as.Date(USD_AUD[['Date']],format = "%d/%m/%Y")
USD_JPY[['Date']]<- as.Date(USD_JPY[['Date']],format = "%d/%m/%Y")
Dow_Jones[['Date']]<- as.Date(Dow_Jones[['Date']],format = "%d/%m/%Y")
Nikkei_225[['Date']]<- as.Date(Nikkei_225[['Date']],format = "%d/%m/%Y")
FTSE_100[['Date']]<- as.Date(FTSE_100[['Date']],format = "%d/%m/%Y")

```




```{r}
#filtering data
a = USD_GBP %>% filter(Date >= '1982-01-01')
b = USD_AUD %>% filter(Date >= '1982-01-01')
c = USD_JPY %>% filter(Date >= '1982-01-01')
d = Dow_Jones %>% filter(Date >= '1982-01-01')
d = d %>% filter(day(Date) ==1)
e = Nikkei_225 %>% filter(Date >= '1982-01-01')
f = FTSE_100 %>% filter(Date >= '1982-01-01')
new_f = seq(as.Date('1982-01-01'),as.Date('2001-01-01'),by = 'month')
df = data.frame(Date = new_f)
f = bind_rows(f,df)
a = select(a,Price,Date)
b = select(b,Price,Date)
c = select(c,Price,Date)
d = select(d,Price,Date)
e = select(e,Price,Date)
f = select(f,Price,Date)







```


```{r}
#plotting graphs

ggplot()+
  geom_line(data = a, aes(x = Date, y=Price))+ggtitle('USD_GBP')


```

this is a  plot of the currency exchange between USD and the British pound
```{r}
ggplot()+
  geom_line(data = b, aes(x = Date, y=Price))+ggtitle('USD_AUD')
```

this is a  plot of the currency exchange between USD and the AUD

```{r}
ggplot()+
  geom_line(data = c, aes(x = Date, y=Price))+ggtitle('USD_JPY')
```

this is a  plot of the currency exchange between USD and the Yen

```{r}
ggplot()+
  geom_line(data = d, aes(x = Date, y=Price))+ggtitle('Dow_Jones')
```

this is a  plot of the Dow Jones stock prices 
```{r}
ggplot()+
  geom_line(data = e, aes(x = Date, y=Price))+ggtitle('Nikkei_225')

```

this is a  plot of the Nikkei 225 stock prices

```{r warning=FALSE}
ggplot()+
  geom_line(data = f, aes(x = Date, y=Price))+ggtitle('FTSE_100')
```

this is a  plot of the FTSE 100 stock prices



```{r}
#refiltering the data

GBP = USD_GBP %>% filter(Date >= '2001-02-01')
AUD= USD_AUD %>% filter(Date >= '2001-02-01')
JPY= USD_JPY %>% filter(Date >= '2001-02-01')
DowJones = Dow_Jones%>% filter(Date >= '2001-02-01')
DowJones =  DowJones%>% filter(day(Date) ==1)
Nikkei = Nikkei_225%>% filter(Date >= '2001-02-01')
FTSE = FTSE_100 %>% filter(Date >= '2001-02-01')
a = select(GBP,Price)
b = select(AUD,Price)
c = select(JPY,Price)
d = select(DowJones,Price)
e = select(Nikkei,Price)
f = select(FTSE,Price)


```

```{r warning=FALSE}
#correlation test to produce a hypothesis test
test1 <- data.frame(c('USD_GBP'=a,'USD_AUD'=b,'USD_JPY'=c,'Dow_Jones'=d,'Nikkei_225'=e,'FTSE_100'=f))

correlation::correlation(test1,include_factors = TRUE, method = "auto")

```
Null hypothesis = no correlation present
Alternate hypothesis = correlation present.
since all pairs except 3 of them  have a p value less that 0.1% showing that their is strong evidence to reject the null hypothesis.


```{r}
#GBP comparisons:
summary(lm(GBP$Price~AUD$Price)) #Regression equation - y = 0.15x + 0.47
summary(lm(GBP$Price~JPY$Price))#Regression equation - y = 0.002x+0.45
summary(lm(GBP$Price~DowJones$Price))#Regression equation - y = 8.38e-06x + 5.18e-01
summary(lm(GBP$Price~Nikkei$Price))#Regression equation - y = 9.09e-06x +  5.14e-01
summary(lm(GBP$Price~FTSE$Price))#Regression equation - y = 4.96e-05x + 3.63e-01
```
The best comparison for this dataset was GBP against Dow Jones.This creates the regression formula of y = 8.38e-06x + 5.18e-01.The R squared value for this comparison is 0.54 showing that the model has a goodness fit of 54%. This R squared value is greater than 50% which shows that it is a good model for the dataset.The p value for this analysis is less than 2.2e-16 and since this is smaller than the significance level of 5% I can reject the null hypothesis.

```{r}
#AUD comparisons:
summary(lm(AUD$Price~GBP$Price))#Regression equation - y = 0.94x +0.70
summary(lm(AUD$Price~JPY$Price))#Regression equation - y = 0.01x + 0.13
summary(lm(AUD$Price~DowJones$Price))#Regression equation - y = 2.51e-06x + 1.29
summary(lm(AUD$Price~Nikkei$Price))#Regression equation - y = 5.90e-06x +1.23
summary(lm(AUD$Price~FTSE$Price))#Regression equation - y = -3.51e-05x +1.54
```
The best comparison for USD_AUD was with the dataset USD_JPY.These coefficients produce a regression line y = 0.01x + 0.13.The R squared value for these datasets in 0.48 which means that the goodness fit of the model is 48%.For the hypothesis test the p value for this analysis is less than 2.2e-16 and since this is smaller than the significance level of 5% I can reject the null hypothesis.
```{r}
#JPY comparisons:
summary(lm(JPY$Price~GBP$Price))#Regression equation - y = 50.86x + 75.53
summary(lm(JPY$Price~AUD$Price))#Regression equation - y = 43.55x +51.31
summary(lm(JPY$Price~DowJones$Price))#Regression equation - y = 7.37e-04 + 9.65e+01
summary(lm(JPY$Price~Nikkei$Price))#Regression equation - y = 1.33e-03x+ 8.74e+01
summary(lm(JPY$Price~FTSE$Price))#Regression equation - y = 4.07e-03x + 8.46e+01
```
The best comparison for USD_JPY was with the dataset USD_AUD.These coefficients produce a regression line of y = 43.55x +51.31.The R squared value is 0.48 showing that the model has a goodness fit of 48%.. For the hypothesis test the p value for this analysis is less than 2.2e-16 and since this is smaller than the significance level of 5% I can reject the null hypothesis.
```{r}
#Dow_Jones comparisons:
summary(lm(DowJones$Price~GBP$Price))#Regression equation - y = 65018x -25775
summary(lm(DowJones$Price~AUD$Price))#Regression equation - y = 3016x+13334
summary(lm(DowJones$Price~JPY$Price))#Regression equation - y = 222.41-6953.54
summary(lm(DowJones$Price~Nikkei$Price))#Regression equation - y= 1.21x - 2.50e+03
summary(lm(DowJones$Price~FTSE$Price))#Regression equation - y = 6.32x -2.09e+04
```
The best comparison for Dow_Jones was with the dataset Nikkei_225.These values create a regression line of y= 1.21x - 2.50e+03.The R squared value is 0.90 meaning that comparison  has a  high goodness fit of 90%.For the hypothesis test the p value for this analysis is less than 2.2e-16 and since this is smaller than the significance level of 5% I can reject the null hypothesis.
```{r}
#Nikkei_225 comparisons:
summary(lm(Nikkei$Price~GBP$Price))#Regression equation - y = 43680x -12538
summary(lm(Nikkei$Price~AUD$Price))#Regression equation - y = 4328x +10601
summary(lm(Nikkei$Price~JPY$Price))#Regression equation - y=248.85x -10756.58
summary(lm(Nikkei$Price~DowJones$Price))#Regression equation - y = 7.48e-01x +3.46e+03
summary(lm(Nikkei$Price~FTSE$Price))#Regression equation - y = 5.00x - 1.39e+04
```
The best comparison for Nikkei_225 was with the dataset Dow_Jones.These values create a regression line y = 7.48e-01x +3.46e+03.The R squared value is 0.90 meaning that comparison  has a  high goodness fit of 90%.For the hypothesis test the p value for this analysis is less than 2.2e-16 and since this is smaller than the significance level of 5% I can reject the null hypothesis
```{r}
#FTSE_100 comparisons:
summary(lm(FTSE$Price~GBP$Price))#Regression equation - y = 6281.1x + 1895.2
summary(lm(FTSE$Price~AUD$Price))#Regression equation - y = -687.8x + 6976.4
summary(lm(FTSE$Price~JPY$Price))#Regression equation - y = 20.04x + 3871.11
summary(lm(FTSE$Price~DowJones$Price))#Regression equation - y = 1.03e-01x + 4.27e+03
summary(lm(FTSE$Price~Nikkei$Price))#y = 1.32e-01x + 3.89e+03
```
The best comparison for FTSE_100 was with the dataset Nikkei_225.The regression line for this pair is y = 1.32e-01x + 3.89e+03.The R squared is calculated to be 0.66 meaning that this model has a fit of 60%.For the hypothesis test the p value for this analysis is less than 2.2e-16 and since this is smaller than the significance level of 5% I can reject the null hypothesis.